Capstone Movielens Report

### 2025-09-21 reports/capstone-movielens.site/01.intro.Rmd
Working on Conclution section (in progress)
Refactoring: in progress...
Fix for Intro section.

# Introduction / Overview / Executive Summary

@@

Our goal is to achieve a value of less than 0.86490 (compare with the _Netflix Grand Prize_ requirement: of at least 0.8563[@BigChaosSln]). 
\newpage

@@

To start with we have to generate two datasets derived from the _MovieLens_ one mentioned above:

@@

For this purpose the following package has been developed by the author of this report: `edx.capstone.movielens.data`. The source code of the package is available [on GitHub](https://github.com/AzKurban-edX-DS/edx.capstone.movielens.data)[@edx_capstone_movielens_data].

>>>>

# Overview and Executive Summary {#intro}

@@

Our goal is to achieve a value of less than 0.86490 (compare with the _Netflix Grand Prize_ requirement: of at least 0.8563[@BigChaosSln]).

@@

To start with we have to generate two datasets derived from the _MovieLens_ dataset mentioned [above](#intro):

@@

For this purpose, a dedicated package, [edx.capstone.movielens.data](https://github.com/AzKurban-edX-DS/edx.capstone.movielens.data), has been developed by the author of this report. The source code of the package is available on [GitHub](https://github.com/AzKurban-edX-DS/edx.capstone.movielens.data)[@edx_capstone_movielens_data].
